What's hot and what's not:\\Windowing developer topic analysis

### 2009-04-10 lda-paper.tex
in the middle of hacking some numbers

The largest common trend has references to build system files like
SYSDD.punix and MONITOR.punix etc. Other tokens mentioned are Sutcheck
v1.09, the prefix SUT stands for Storable Unit Type. Sutcheck would
also automate check-ins using a Perforce SCS tool.

The second largest common trend seems to be a side effect of an
automated check-in which is annotated as ``implicit check-in''. These
were check-ins that were produced when importing changes from an
external Perforce repository.

The third most common trend, seen on Figure \ref{fig:trendtimeline}, seemed to
include tokens related to operating system support, such as Linux and
Windows, as well as architecture support, AMD64 and Opteron. The word
problem was common among all of those trends. This trend seemed
related to the smaller fourth largest trend which occurred nearby it
that had AMD64 and Windows tokens.

@@

The query optimizer was a topic which recurred multiple times during
MaxDB's development. In our plots, topics which mention optimizer
occur four times yet in the large static plot (Figure
\ref{fig:statictopics}) it is not in any of the topics. A query
optimizer is rather important to an DBMS, but as we've shown it just
doesn't pop up as a topic on its own. We tried to remove words to see
if we could get optimizer topic out, after removing stop words and
then two of the most common words the global analysis finally had a
topic with optimizer in its topic ten words. This shows that optimizer
was important but it had been obscured, while it would have been
noticed using a more locally relevant approach that we propose.

@@

@@

>>>>

The largest common trend has references to build system files like
SYSDD.punix and MONITOR.punix.  This trend is partially displayed at
the top of the zoomed in compressed view plot (Figure
\ref{fig:zoomedsmear}) and at the top of the histogram plot (Figure
\ref{fig:histogram}).  Other tokens mentioned are Sutcheck v1.09, the
prefix SUT stands for Storable Unit Type. Sutcheck would also automate
check-ins using a Perforce SCS tool which was exported to CVS.

The second largest common trend seems to be a side effect of an
automated check-in which is annotated as ``implicit check-in'' (see
the bottom of Figure \ref{fig:zoomedsmear}). These were check-ins that
were produced when importing changes from an external Perforce
repository.

The third most common trend, seen on Figure \ref{fig:trendtimeline},
seemed to include tokens related to operating system support, such as
Linux and Windows, as well as architecture support, AMD64 and
Opteron. The word \emph{problem} was common among all of these
trends. This trend seemed related to the smaller fourth largest trend
which occurred nearby which referenced tokens \emph{AMD64} and
\emph{Windows}, this shows that topics can overlap but still not match
via our similarity measure.

@@

The query optimizer was a topic which recurred during
MaxDB's development. In our plots, topics which mention optimizer
occur four times yet in the large static plot (Figure
\ref{fig:statictopics}) it is not in any of the topics. A query
optimizer is rather important to an DBMS, but as we've shown it just
doesn't pop up as a topic on its own. We tried to remove words to see
if we could get optimizer topic out, after removing stop words and
then two of the most common words the global analysis finally had a
topic with optimizer in its topic ten words. This shows that optimizer
was important but it had been obscured, while it would have been
noticed using a more locally relevant approach that we propose.

@@

UNICODE

DEC/OSF1

ODBC

crash

% PHP yet Perl is mentioned is less but it part

SQLCLI
%V75

SYSDD.cpnix
backup

select
make
memory
view

debug

% V75 is mentioned many times maxdb version guh

@@

If we approach the difference via common tokens we can see that common
token tend to dominate both results, at least in the case of MaxDB
7.500 our local topic approach netted us topics which contained these
relatively important and common words: \emph{UNICODE},
\emph{DEC/OSF1}, \emph{ODBC}, \emph{crash}, \emph{SQLCLI},
\emph{SYSDD.cpnix}, \emph{backup}, \emph{select}, \emph{make},
\emph{memory}, \emph{view}, and finally \emph{debug}. None of these
tokens were part of the static topic analysis topics but they were
part of 494 commits (5\% of the entire system) to MaxDB 7.500.

% Revisions 26+1+103+19+20+48+35+50+77+49+48+18
% Revisions 494 
% Topics 1+1+19+1+5+10+7+10+11+9+9+7
% Topics 90
